HO unification from object language to meta language

### 2024-03-20 paper/main.tex
fix

\subsection{The intuition in a nutshell}
\label{sec:nutshell}
A term $s$ is compiled in a term $t$ where any
``problematic'' subterm $tp$ is replaced by a fresh unification variable $h$
and an accessory link that represent a suspended unification problem
$h \Ue tp$. As a result \Ue is ``well behaved'' on $t$, meaning it does not
contradict \Eo (as it would do on ``problematic'' terms).
We now define ``problematic'' and ``well behaved'' more formally.

@@

\begin{proposition}[\wellb{}-preservation]\label{prop:nf}
$\forall \mathcal{T}, \forall \mathbb{L}, \forall p, \forall \sigma, \forall \sigma'$
$$
\wellb(\sigma\mathcal{T}) \land
\stepH{\mathcal{T}}{p}{\sigma}{\mathbb{L}}{\sigma'}
\Rightarrow \wellb((\sigma \cup \sigma')\mathcal{T})
$$
\end{proposition}

>>>>

\subsection{The intuition in a nutshell}
\label{sec:nutshell}
A term $s$ is compiled in a term $t$ where any
``problematic'' subterm $p$ is replaced by a fresh unification variable $h$
and an accessory link that represent a suspended unification problem
$h \Ue p$. As a result \Ue is ``well behaved'' on $t$, meaning it does not
contradict \Eo (as it would do on ``problematic'' terms).
We now define ``problematic'' and ``well behaved'' more formally.

@@

\begin{proposition}[\wellb{}-preservation]\label{prop:nf}
$\forall \mathcal{T}, \forall \mathbb{L}, \forall p, \forall \sigma, \forall \sigma'$
$$
\wellb(\sigma\mathcal{T}) \land
\stepH{\mathcal{T}}{p}{\sigma}{\mathbb{L}}{\sigma'}
\Rightarrow \wellb(\sigma' \mathcal{T})
$$
\end{proposition}
